Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Url formatting, references

\bibitem{lantmateriet-19}
Lantmäteriet. (2019). Produktbeskrivning: GSD-Fastighetskartan vektor. Acessed 16-04-2020. \\ 
https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf.

\bibitem{osm-19}
OSM. (2019). Converting to WGS84 - OpenStreetMap Wiki. Accessed 13-03-2020. \\ 
https://wiki.openstreetmap.org/wiki/Converting\_to\_WGS84.

\bibitem{osm-20}
(OSM 20) OSM History Viewer - OpenStreetMap Wiki. Accessed 20-03-2020. \\
https://wiki.openstreetmap.org/wiki/OSM\_History\_Viewer.

>>>>

\bibitem{lantmateriet-19}
Lantmäteriet. (2019). Produktbeskrivning: GSD-Fastighetskartan vektor. Acessed 16-04-2020.
https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf.

\bibitem{osm-19}
OSM. (2019). Converting to WGS84 - OpenStreetMap Wiki. Accessed 13-03-2020.
https://wiki.openstreetmap.org/wiki/Converting\_to\_WGS84.

\bibitem{osm-20}
OSM. (2020). OSM History Viewer - OpenStreetMap Wiki. Accessed 20-03-2020
https://wiki.openstreetmap.org/wiki/OSM\_History\_Viewer.
